---
title: "Notebook for equity data visualization"
output: html_notebook
---

Import the common scripts, modules and libraries and set the working directory.

```{r}
setwd("/home/neehan/data/Nafis/ESCA_Git")
source("./Scripts/common.R")
source("./Scripts/run_patt_scenario.R")
source("./Modules/p_val_add.R")
source("./Modules/equity_metrics_miao.R")
```

Import the result file that contains the LDM Summary. It was generated using 'generate_ldm_data.rmd' notebook.

```{r}
setwd("/home/neehan/data/Nafis/ESCA_Git")
directory <- "./Data/Results/M6/"
filename <- "LDM_Summary.csv"
Final_PATT_Summary <- read.csv(paste(directory, filename, sep = ""))
```

Some of the equity variables (Race, Gender, Age) might have missing subgroups in one or more populations (CC Size). That results in Infinity when we calculate equity. Here I replace the infinities with max_value + 0.5 where max_value is the maximum value in the whole Final LDM Summary matrix. So all infinite values are replaced with one specific value. We do this to retain the information of which subgroups are still missing. This helps with the case that synthetic control arms are helping with compensating for missing subgroups.

```{r}
Inf_replace <- max(Final_LDM_Summary %>% mutate_all(function(x) ifelse(is.infinite(x), -1, x)) %>% 
                     select(LDM_CC:LDM_HC_Prop_IPF)) + 0.5
LDM_Summary_Inf <- Final_LDM_Summary
LDM_Summary_Inf[sapply(LDM_Summary_Inf, is.infinite)] <- Inf_replace

```

Now take median across all 20 scenarios (scenario = seed value), and calculate confidence intervals.

```{r}
mean_summary <- LDM_Summary_Inf %>%
  group_by(CC_Size, Level) %>%
  summarise(median(LDM_TA),
            LDM_TA_Low = confidence_interval(unlist(LDM_TA), 0.95)[1],
            LDM_TA_High = confidence_interval(unlist(LDM_TA), 0.95)[2],
            median(LDM_CC),
            LDM_CC_Low = confidence_interval(unlist(LDM_CC), 0.95)[1],
            LDM_CC_High = confidence_interval(unlist(LDM_CC), 0.95)[2],
            median(LDM_HC_Prop),
            LDM_HC_Prop_Low = confidence_interval(unlist(LDM_HC_Prop), 0.95)[1],
            LDM_HC_Prop_High = confidence_interval(unlist(LDM_HC_Prop), 0.95)[2],
            median(LDM_HC_IPF),
            LDM_HC_IPF_Low = confidence_interval(unlist(LDM_HC_IPF), 0.95)[1],
            LDM_HC_IPF_High = confidence_interval(unlist(LDM_HC_IPF), 0.95)[2],
            median(LDM_TA_Prop_IPF),
            LDM_TA_Prop_IPF_Low = confidence_interval(unlist(LDM_TA_Prop_IPF), 0.95)[1],
            LDM_TA_Prop_IPF_High = confidence_interval(unlist(LDM_TA_Prop_IPF), 0.95)[2],
            median(LDM_HC_Prop_IPF),
            LDM_HC_Prop_IPF_Low = confidence_interval(unlist(LDM_HC_Prop_IPF), 0.95)[1],
            LDM_HC_Prop_IPF_High = confidence_interval(unlist(LDM_HC_Prop_IPF), 0.95)[2],
  ) %>%
  rename(LDM_TA = "median(LDM_TA)",
         LDM_CC = "median(LDM_CC)",
         LDM_HC_Prop = "median(LDM_HC_Prop)",
         LDM_HC_IPF = "median(LDM_HC_IPF)",
         LDM_TA_Prop_IPF = "median(LDM_TA_Prop_IPF)",
         LDM_HC_Prop_IPF = "median(LDM_HC_Prop_IPF)") %>%
  mutate(LDM_CC_Low = ifelse(LDM_CC==Inf_replace, LDM_CC, LDM_CC_Low),
         LDM_CC_High = ifelse(LDM_CC==Inf_replace, LDM_CC, LDM_CC_High)) %>%
  mutate(Plot = ifelse(LDM_CC==Inf_replace, paste(as.character(CC_Size),"*"),
                       as.character(CC_Size))) %>%
  ungroup()
```

Function to generate the plot. This plot generates equity lines for all four populations and plots them in the same graph along with the baseline defined as green dashed line.

```{r}
return_plot <- function(var, level){
  ymin_val <- min(ungroup(mean_summary) %>% filter(Level==level) %>% 
                    select(LDM_CC:LDM_HC_Prop_IPF_High))
  ymax_val <- max(ungroup(mean_summary) %>% filter(Level==level) %>% 
                    select(LDM_CC:LDM_HC_Prop_IPF_High))
  cap <- paste(var,":",level)
  p <- mean_summary %>% filter(Level==level) %>%
    ggplot(aes(x=factor(Plot, levels = mixedsort(Plot)))) +
    geom_line(aes(y=LDM_CC, color="Only CC")) +
    geom_errorbar(aes(ymin=LDM_CC_Low, ymax=LDM_CC_High, colour="Only CC")) +
    geom_point(aes(y=LDM_CC, colour="Only CC")) +
    geom_line(aes(y=LDM_HC_Prop, color="HC+Propensity")) +
    geom_errorbar(aes(ymin=LDM_HC_Prop_Low, ymax=LDM_HC_Prop_High, colour="HC+Propensity")) +
    geom_point(aes(y=LDM_HC_Prop, color="HC+Propensity")) +
    geom_line(aes(y=LDM_HC_IPF, color="HC+IPF")) +
    geom_errorbar(aes(ymin=LDM_HC_IPF_Low, ymax=LDM_HC_IPF_High, colour="HC+IPF")) +
    geom_point(aes(y=LDM_HC_IPF, color="HC+IPF")) +
    geom_line(aes(y=LDM_HC_Prop_IPF, color="HC+Propensity+IPF")) +
    geom_errorbar(aes(ymin=LDM_HC_Prop_IPF_Low, ymax=LDM_HC_Prop_IPF_High, color="HC+Propensity+IPF")) +
    geom_point(aes(y=LDM_HC_Prop_IPF, color="HC+Propensity+IPF")) +
    geom_hline(aes(yintercept= 0.22, color = "Equity Range"), linetype="dashed")+
    #ylim(ymin_val,ymax_val)+
    theme_classic()+
    theme(axis.title =element_text(size=6), axis.text.x = element_text(angle = 90))+
    scale_color_manual(name="Population",
                       values=c("Only CC"="#D55E00", "HC+Propensity"="#336699", "HC+IPF"="#CC66FF",
                                "HC+Propensity+IPF"="#FFCC00", "Equity Range"="#99CC33"))+
    labs(x="CC_Size", y="Median LDM Estimate", caption = cap)
  return (p)
}

```

```{r}
g1 <- return_plot("Gender", "Female")
g2 <- return_plot("Gender", "Male")
a1 <- return_plot("Age_Group", "40-59")
a2 <- return_plot("Age_Group", "59+")
r1 <- return_plot("Race_or_Ethnicity", "NH Asian")
r2 <- return_plot("Race_or_Ethnicity", "NH Black")
r3 <- return_plot("Race_or_Ethnicity", "NH White")
r4 <- return_plot("Race_or_Ethnicity", "Hispanic")
r5 <- return_plot("Race_or_Ethnicity", "Other")
```

```{r warning=FALSE}
ggarrange(g1,g2, nrow=1,
          common.legend = TRUE, legend = "bottom")
```

```{r warning=FALSE}
ggarrange(a1,a2, nrow=1,
          common.legend = TRUE, legend = "bottom")

```

```{r warning=FALSE}
ggarrange(r1, r2, r3, r4, r5, nrow=2, ncol=3,
          common.legend = TRUE, legend = "bottom")

```
